### 2018-07-06 dissertation/6-conclusao/chapter6.tex
small improvement to conclusion

In the coming years, vehicular networks or VANETs will an important part of safety and security in transportation, optimizing traffic and reducing the number of accidents.
However, they are an appealing target for entities with malicious intents, creating the need of robust solutions to maintain the integrity of such networks.

@@

>>>>

In the coming years, vehicular networks or VANETs will be an important part of safety and security in transportation, optimizing traffic and reducing the number of accidents.
However, they are an appealing target for entities with malicious intents, creating the need of robust solutions to maintain the integrity of such networks.

@@

In comparison with the related work, TruMan was able to satisfy most of the desired properties for vehicular network trust models, while not inhibiting the properties that were not desired.
Most importantly, TruMan put emphasis on efficiency and is the first model that clearly displays the complexity of its algorithm.

The work done on TruMan was published as a conference paper on the 2018 IEEE Symposium on Computers and Communications \citep{greca2018truman}.
